\section{User Stories for the My Technology Tutor App, being presented Team: Peanut The Amazing Programmer}

\subsection{Here we will present 4 User Stories for our App, using the IMPACT Template of Writing User Stories!}
\subsubsection{As a refresher, here is the basic of the IMPACT Template of writing User Stories:}
\begin{enumerate}
\item INVEST: The attributes of a solid user story
\item INVEST is an acronym that helps evaluate whether you have a high-quality user story.
\item Here's how the attributes in the acronym apply to the story we've been working on.
\item I = Independent|Can this story be completed by the team? We want the team to
be able to complete the whole story rather than be dependent on a dierent team to
do the GUI, for example.
\item N = Negotiable|The story is not so detailed as to describe exactly how long the elds
should be or give specics about date formats and the like. Most likely there will be
common routines or libraries that will allow the development team to implement in
the way that makes the most sense for them.
\item V = Valuable|The product owner describes that the value being sought is the ability
for the trainer to be able to advertise upcoming classes. This is clear in the "why" of
the original statement and re-emphasized in the conversation.
\item E = Estimable|The team will ask enough questions and gather the details to feel
condent in their ability to estimate the story.
\item S = Small|The team needs to feel condent that they'll be able to complete the
story within a sprint. If they do not, they might split the story. For instance, in our
sample story, they may decide to make the ability to gather the student information
be a different story and simply display information about the class for this story.
\item T = Testable|With clear acceptance criteria, both the happy path and error conditions can be tested.
\end{enumerate}

\section{User Story 1}
\item Description of USER STORY:
\item My user SHALL have the ability to view all the courses which are available at their current level of progress 
\item The user shall have the ability TO ADD A COURSE to their profile, and start the course
\item The user shall the the ability to resume any in-progress course in a subsequent session, until completed.
\item The Profile shall Display the user's completed courses and their score.
\item: Value: The user is getting the confidence of progressing through a guided set of learning activities, and the satisfaction of seeing their grade at the end. 
\item: TESTABLE: I can use Scenario-based testing to ensure the product is implementing the User Story as I have written it.

